% !TeX spellcheck = en_US
\chapter{Variational Autoencoders}

\section{Basics Definitions}
\label{sec:vae-defs}
\begin{itemize}
	\item \textit{Probabilistic model}: is a model that represents a probability distribution. It could be a marginal \ac{prob} distribution $p(x)$ or a conditional \ac{prob} distribution $p(y|x)$.
	\item \textit{Evidence, query, and latent variables}:\\
	The word \hlb{latent} implies existing, but hidden. \Eg"
	\begin{itemize}
		\item In $p(x)$, $x$ is the query variable and there is no evidence variable.
		\item In $p(y|x)$, $y$ is the query variable and $x$ is the evidence variable.
		\item In \ac{MoG} $p(x) = \sum_z p(x|z) p(z)$, $x$ is the query variable, $z$ is the latent variable to represent the mixture elements.		
		\item In $p(y|x) = \sum_z p(y|x,z) p(z)$, $z$ is the latent variable.
		\item In a neural network, the inputs are evidence variables, the output are the query variables, and all \ac{param} for the hidden layers can be considered as latent variables, though that would not be a helpful way of consideration. In \ac{VAE}, only $z$ is considered as the latent variable with a simple Gaussian distribution.
		\item In model-based \ac{RL} with latent variable models, $x_t$ is the latent variable.
	\end{itemize}
	\item \textit{Latent variable models}: is the type of probabilistic model that represent a complex \ac{pdf} as the product of multiple simpler \ac{pdf}s, one of which belongs to a latent variable. \Eg: in \ac{VAE}, we has $p(z)$ as an \textit{easy} \ac{pdf} (\eg, Gaussian), $p(x|z)$ as a learnable neural network, then we represent the complex $p(x)$ as:
	\[ p(x) = \int p(x|z) p(z) dz \]
\end{itemize}

\section{Variational Inference}
This section describes how to calculate $p(z|x_i)$

\section{References}
\begin{itemize}
	\item \href{https://www.youtube.com/watch?v=5WoItGTWV54}{Generative models | CS231, Stanford | YouTube}
	\item \href{https://www.youtube.com/watch?v=9zKuYvjFFS8}{Variational Autoencoders | Arxiv Insights | YouTube}
	\item \href{https://www.youtube.com/watch?v=fcvYpzHmhvA}{Variational Autoencoders | CodeEmporium | YouTube}
	\item \href{https://github.com/vdumoulin/conv_arithmetic}{Real "deconv" layer | GitHub}
\end{itemize}